% Declarations for Front Matter

% MS Thesis = 0, Phd Dissertation = 1
\isdissertation{1}

% electronic submission? Paper only = 0, Electronic = 1
\iselectronic{1}

\title{Exploring Spatial Patterns of Genetic Differentiation}
\author{Gideon S. Bradburd}

% Choices are September, December, March, June
\degreemonth{September}
\degreeyear{2015}
%More examples DOCTOR OF PHILOSOPHY
\degree{Doctor of Philosophy}

\chair{Graham Coop}
\othermembers{{Brad Shaffer, Chair},Brian Moore} %comma separated list of committee not including chair
\numberofmembers{3} % size of committee

\prevdegrees{B.S (Yale University) 2008}

%Your Graduate Group
\field{Population Biology}
\campus{Davis}


% add the abstract here
\input{abstract}

%Not required for electronic submission, you will need to print your other abstract page 2x and hand them in.
% Here is the first, external, abstract.
%\begin{abstract}
%	\myabstract
%	\abstractsignature
%\end{abstract}

\begin{frontmatter}
\maketitle

% A copyright page is optional. If you have one, it must immediately
% follow the title page. For more information about the copyright page
% see the UCD's Office of Graduate Studies web site.
% \copyrightpage

% dedication (optional), remove comment markers to use 
%\begin{dedication}
%\null\vfil
%{\large
%\begin{center}
%xxxx
%\end{center}}
%\vfil\null
%\end{dedication}



\tableofcontents
\listoffigures
\listoftables

% Here is the second, internal, abstract.
% Update: Melissa Danforth 2006
% Inline abstract is now part of front matter according to coordinator
    \newpage
    \begin{inlineabstract}
		%Only enable small if you're trying to make it fit.		
		%\begin{small}
		\myabstract
		%\end{small}
		
    \end{inlineabstract}

%Acknowledgments (optional)
\begin{acknowledgments}
\par I am incredibly lucky to have had Graham Coop and Brad Shaffer as my co-advisors.  Their unending enthusiasm for science, coupled with the depth of knowledge they hold in their fields, made my PhD experience exciting and rewarding.  They have been exceptional mentors, and they are and will remain my role models as scientists and human beings.
%%
\par I am also grateful to Brian Moore for being on my committee and for the knowledge and friendship and support, and to the academic counsel of Anurag Agrawal, Dave Begun, Janet Foley, Rick Grosberg, Richard McElreath, Santiago Ramirez, Jeff Ross-Ibarra, Sebastian Schrieber, Annie Schmitt, Mark Schwartz, Jay Stachowicz, Mau Stanton, Sharon Strauss, Michael Turelli, Peter Wainwright, and Louie Yang.  It truly takes a village.
%%
\par Yaniv Brandvian, D. Luke Mahler, and Peter Ralph were three outstanding people with whom I had the good fortune to overlap while at Davis.  I  owe all three a massive debt of gratitude for their endless patience and snacks, and for reading many, many drafts of grants and papers, and for being all around awesome.
%%
\par Peter Bull and Will Wetzel are two of the finest individuals I know, and their wisdom and friendship and high fives were simply the best.  Thanks to both for being the Samwises to my Frodo while I struggled up the mountain.
%%
\par I am a scientist because of my wonderful parents, Ralph and Zelda, who were so encouraging of their ``didacti-boy," and who taught me to read, and also because of my big sibling B, who continues to teach and show me how to be a better person.
%%
\par Finally, and most importantly, I would like to thank my favorite scientist, Dr. Marjorie Weber.  Her brilliance, curiosity, and passion inspire everyone around her, especially me.  Marge gave unending patience, support, help with coming up with acronyms for statistical methods, and love.   This dissertation is dedicated to her.

\end{acknowledgments}

%Preface (optional)
%\chapter*{Preface}
%\addcontentsline{toc}{chapter}{Preface}
%\input{preface}


\end{frontmatter}
